\chapter{Social Media and Politics}\label{ch:SMandPolitics}

\section{Political Communication in the Digital Era}

Technological innovation often precedes political disruption; Martin Luther’s 95
theses could only be spread at scale by virtue of Gutenberg inventing his
printing press first \cite{gardels2019renovating}. This example had obvious
political ramifications and is a testament to the impact of the means of
communication on the political sphere. McNair defines political communication
as:

\begin{enumerate}
    \item All forms of communication undertaken by politicians and other
    political actors for the purpose of achieving specific objectives.
    \item Communication addressed to these actors by non-politicians such as
    voters and newspaper columnists.
    \item Communication about these actors and their activities, as contained in news reports, editorials, and other forms of media discussion of politics. \cite{mcnair2017introduction}
\end{enumerate} 

This is a broad, outward focused definition that includes most public, political
discourse - verbal or otherwise. However, social media has changed all three
aspects of this definition in novel ways. Most notably, the rate at which
politicians can communicate information to achieve “specific objectives” has
increased as a result of rapid nature of social media, and the granularity at
which actors can target the these messages has gotten smaller due to the massive
swaths of user data available \cite{nickerson2014political}. Therefore, the
value of using computational methods to study political communication in the
$21^{st}$ century is a natural fit.

\subsection{Technology's Implications for Democratization}

While fully exploring the impact of social media on democracy is out of the
scope of this project, it is an important justification for why research in this
area needs to be conducted. The traditional model of the media being a mediating
force through their reporting, commentary and analysis is no longer valid.
Previously, political actors needed to use the media to broadcast their messages
to their desired audiences \cite{mcnair2017introduction}. Social networking
sites allow these same actors to reach audiences in the millions without having
to gain access to the media first; in this effect, the second and third elements
of McNair’s definition are also being transformed. Yascha Mounk argues that this
has given voice to political outsiders who would be shut out from mainstream
platforms. Thus, social media may not be inherently democratic or undemocratic,
as it has contributed to democratic backsliding and overturning authoritarian
governments, but it can certainly have a destabilizing affect
\cite{mounk2018people}. Therefore, a better understanding of new media’s
ramifications is critical, and empirical modeling can aide in this
understanding.

\section{Canadian Brokerage Politics}

While it is clear that technology is changing how information is received, and
thus must also be changing how politics is conducted, it may not be clear the
role of Canadian politics in this research. However, Canada’s political system
is the perfect environment to test the importance of political messaging, be-
cause relative to most liberal democracies, the system is dominated by party
politicians. As Carty put it:

\begin{quote}
No obvious simple geographic reality, no common linguistic or religious
homogeneity, no common revolutionary experience or unique historical moment
animated [Canada] or gave it life. Canada was created when a coalition of party
politicians deemed it to be in their interest to do so, and it has been
continuously grown, reshaped and defended by its politicians.
\cite{carty2010political}
\end{quote}

Thus, it is not surprising that Canada’s electoral system encourages electoral
pragmatism - and developed large, “big tent” parties that are among the most
organizationally weak and decentralized of established democracies
\cite{carty2010political}. This system defines political parties as brokers of the
often conflicting, weakly integrated electorate - as opposed to mobilizers of
distinct communities, articulating claims rooted in their pre-existing
interests. In this way, parties act as the principal instruments of national
accommodation, rather than democratic division \cite{carty2010political}.

\subsubsection{Rationale}

The dominance of parties in Canadian politics, their amorphous ideological
stances, and the many intersectional geographic, linguistic and religious
cleavages have given birth to what’s been coined the brokerage party system.
\cite{carty2010political}. The need to capture pluralities in a diverse range of
electoral districts gives Canada a unqiue set of dynamics - making it an
interesting case to explore.